\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-06 paper-two/paper-two.tex
paper 2: adding all new images, with new renders

\begin{figure}[H]
  \centering
  \includegraphics[width=7.5cm]{images/top-dmn-sn-cen-switching.jpg}
  \caption{The Salience Network consists of the Anterior Cingulate Cortex and the
    Anterior Insular Cortex. It helps switch between the Default Mode Network and the
  Central Executive Network.}
  \label{fig:top-dmn-sn-cen-switching}
\end{figure}

@@

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/top-cen.jpg}
  \caption{The Central Executive Network.}
  \label{fig:top-cen}
\end{figure}

@@

@@

@@

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=7.5cm]{images/fmri-switching.jpg}
  \caption{The Salience Network consists of the Anterior Cingulate Cortex and the
    Anterior Insular Cortex. It helps switch between the Default Mode Network and the
  Central Executive Network.}
  \label{fig:fmri-switching}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-dmn.jpg}
  \caption{fMRI scan of the Default Mode Network.}
  \label{fig:fmri-dmn}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-cen.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-cen.png}
  \end{subfigure}
  \caption{Highlighted: areas of the brain firing when the Central Executive Network is active.}
  \label{fig:cen}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-cen.jpg}
  \caption{fMRI scan of the Central Executive Network.}
  \label{fig:fmri-cen}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-sn.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-sn.png}
  \end{subfigure}
  \caption{Highlighted: areas of the brain firing when the Salience Network is active.}
  \label{fig:sn}
\end{figure}

\todo{Are the labels on either the SVG or the MRI image reversed?}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/fmri-sn.jpg}
  \caption{fMRI scan of the Salience Network.}
  \label{fig:fmri-sn}
\end{figure}
